\thetitle

### 2024-11-19 paper/paper.tex
Flesh out more of the rewrite.

TODO: Discuss \citet{riess1998}, \citet{perlmutter1999}, and \citet{perlmutter2003}, as well as their nobel prize, summarized in \citet{straumann2012}.

Summarize dark energy. Emphasize that dark energy is a popular explanation for
why distant supernova appear to be too far away.

Talk about the difficulty of curating supernova data, and summarize the work
done by \citet{betoule2014}.

@@

The characteristics of redshift depend on the reason distant objects are
redshifted. The dominant model is the big bang theory, where the farther away
an object is from us, the more quickly it is moving away from us. Another
theory is the tired light hypothesis, as described by \citet{shao2013}, where
distant objects are mostly stationary relative to us, but where the energy of
light is lost as it travels through space. A feature of the tired light
hypothesis is that since distant objects do not have a high relative velocity
to us, they should not show time dilation. However, as shown by
\citet{white2024}, distant supernova do experience time dilation. Based on
this, we reject the tired light hypothesis and assume the big bang model.

@@

In the big bang model, there are two phenomena associated with redshift that we
might expect to reduce the appearant magnitude of a Type Ia supernova. The
first phenomenon is that the energy carried by a photon is inversely
proportional to wavelength, so as redshift increases the wavelength of a
photon, the energy decreases. The second phenomenon is that time dilation for
objects moving quickly relative to our observational rest frame will reduce the
rate at which photons are being emitted.

The supernova data collected by the DES Collaboration used a CCD camera, a
photon counting device, as described by \citet{flaughter2015}.  As noted by
\citet{kim1996}, photometric measurements that depend on bolometers will need
to be corrected for the reduced energy level of redshifted light, but with a
photon counting device, this correction is not necessary.

However, time dilation also reduces the magnitude of light. Instead of changing
the properties of individual photons, it reduces the count of photons by a
factor of $\frac{1}{1+z}$. This phenomenon will not be addressed by the nuances
of any measuring device, so it must be explicitly corrected.

@@

To derive the luminosity distance from these measurements, we start
by computing the flux $L$. Magnitude $M$ is defined on a logarithmic scale
where magnitude 1 has 100 times the brightness of magnitude 6, leading to

\begin{equation}
  F = \frac{1}{\sqrt[5]{100}^{M - 1}}.
\end{equation}

@@

To compute the corrected magnitue $M^*$, we can solve

\begin{equation}
\begin{aligned}
   F^* &= \frac{1}{\sqrt[5]{100}^{M^* - 1}} \\
   M^* &= M - \frac{\ln{(z + 1)}}{\ln{(\sqrt[5]{100})}}.
\end{aligned}
\end{equation}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/mu_distance_vs_redshift.png}
  \caption{todo}
  \label{fig:corrected_uncalibrated}
\end{figure}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/velocity_vs_distance.png}
  \caption{todo}
  \label{fig:uncorrected_uncalibrated}
\end{figure}

\section{Calibrated distance models}
\label{sec:calibrated}

Calibrating a distance model involves finding a linear regression line for a
model and then computing the value $k$ required to make the regression model
match a Hubble paramater. By arbitrary choice, we use $H_0 = 70 \frac{km/s}{Mpsc}$.

The final units for distance will be in megaparsecs $Mpsc$. To find the
recessional speed for a given redshift, we use $v = cz$ where $c$ is the speed
of light.

To compute a model, we use non-parametric regression via repeated means as described in
\citet{siegel1982}. A comparison of both models is shown in Figure .

@@

Previous studies use $F$ instead of $F*$. According to \citet{betoule2014},

\begin{equation}
  D_L = k 10^\frac{M}{5}.
\end{equation}

\section{Conclusions}
\label{sec:conclusions}

>>>>

TODO.

@@

@@

In the big bang model, there are multiple phenomena associated with redshift that we
might expect to reduce the apparent magnitude of a Type Ia supernova.

\subsection{Recessional velocity redshift}

The energy carried by a photon is inversely proportional to wavelength, given
by the Planck relation

\begin{equation}
  E = \frac{hc}{\lambda}
\end{equation}

where $E$ is energy, $h$ is the Planck constant, $c$ is the speed of light, and
$\lambda$ is the wavelength.

As redshift increases the wavelength of a photon, the energy decreases.

The supernova data collected by the DES Collaboration used a CCD camera, a
photon counting device, as described by \citet{flaughter2015}.  \citet{kim1996}
noted that photometric measurements that depend on bolometers will need to be
corrected for the reduced energy level of redshifted light, but with a photon
counting device, this correction is not necessary.

While the redshift phenomenon should impact the light detected from distant
supernova, it shouldn't impact the magnitude measurements so it does not need
to be explicitly corrected.

\subsection{Time dilation}

The second phenomenon is that time dilation for objects moving quickly relative
to our observational rest frame will reduce the rate at which photons are being
emitted. Instead of changing the properties of individual photons, time
dilation reduces the count of photons by a factor of $\frac{1}{1+z}$.

This phenomenon will not be addressed by the nuances of any measuring device,
so it must be explicitly corrected.

\subsection{Stretching of space}

If space itself is stretching, it will both increase the wavelength of photons
and also reduce the density of those photons. If space is stretching at a
constant rate, the effect would be indistinguishable from the redshift and time
dilation created by high relative recessional velocities. However, an
accelarting expansion of the universe may indicate a non-constant rate of
stretching. This would manifest by distant objects having a greater distance
per redshift than nearby objects.

This non-linear streching-of-space model would be indistinguishable from a
scenario where a constant force is pushing all objects away from each other.

\subsection{Tired light}

And alternative to the big bang theory is the tired light hypothesis, as
described by \citet{zwicky1929} and \citet{shao2013}. The idea is that distant
objects are mostly stationary relative to us, but the energy of light is lost
as it travels through space. A feature of the tired light hypothesis is that
since distant objects do not have a high relative velocity to us, they should
not show time dilation.

However, as shown by \citet{blonden2008} and \citet{white2024}, distant
supernova do experience time dilation. Based on this, we can reject the tired
light hypothesis and assume the big bang model.

@@

To derive the luminosity distance from these measurements, we start
by computing the flux $F$. Magnitude $m$ is defined on a logarithmic scale
where magnitude 1 has 100 times the brightness of magnitude 6, leading to

\begin{equation}
  F = \frac{1}{\sqrt[5]{100}^{m - 1}}.
\end{equation}

@@

To compute the corrected magnitude $m^*$, we can solve

\begin{equation}
\begin{aligned}
   F^* &= \frac{1}{\sqrt[5]{100}^{m^* - 1}} \\
   m^* &= m - \frac{\ln{(z + 1)}}{\ln{(\sqrt[5]{100})}}.
\end{aligned}
\end{equation}

From here, we can use the standard distance modules $\mu$ defined as

\begin{equation}
  \mu = m^* - M
\end{equation}

where $M$ is the absolute magnitude. The luminosity distance $D_L$ in parsecs
can then be calculated as

\begin{equation}
  D_L = 10^{1 + \frac{\mu}{5}}.
\end{equation}

\section{Linear distance vs redshift relationship}

The theory of an accelerating expansion is based on there being a non-linear
relationship between redshift and distance. More specifically, old objects (the
ones that are more distant) should have more distance per redshift than newer
objects.

As shown in Figure \ref{fig:mu_distance_vs_redshift}, this non-linear
relationship is only observed when $k(z) = 1$, meaning that magnitude is not
corrected for time dilation.

In contrast, when $k(z) = 1 + z$, time dilation is accounted for and there is a
linear relationship between redshift and distance. A linear model rules out an
accellerated expansion.

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/mu_distance_vs_redshift.png}
  \caption{The relationship between distance and redshift for two treatments of
  magnitude data. The displayed points are roughly a third of the values in the
  full DES dataset, selected evenly to aid visibility. The $k(z) = 1$ treatment
  is clearly non-linear while the $k(z) = 1 + z$ treatment appears to be
  linear.}
  \label{fig:mu_distance_vs_redshift}
\end{figure}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/velocity_vs_distance.png}
  \caption{The expansion rate of the universe based on the full DES dataset.
  This displays the full DES dataset using $k(z) = 1 + z$. The velocity $v$ is
  calculated from $v = zc$, where $c$ is the speed of light. Note that the axis
  are flipped compared to \ref{fig:mu_distance_vs_redshift}. In a perfectly
  calibrated dataset, the fitted line should match the Hubble constant. This
  graph is based on an absolute magnitude for Type Ia supernova at
  $M = -19.3232$, which yields a slope of about $63 \frac{\text{km/s}}{\text{Mpc}}$.
  If the absolute magnitude of a Type Ia supernova is instead $M = -19.102746$,
  the slope would be $70 \frac{\text{km/s}}{\text{Mpc}}$.}
  \label{fig:uncorrected_uncalibrated}
\end{figure}

@@

Previous studies use $F$ instead of $F*$. To the best of our knowledge, no
studies that depend on the distance of Type Ia supernova, reaching back at
least to \citet{riess1998} and \citet{perlmutter1999}, have accounted for time
dilation.
